---
title: "Pollen Germination"
author: "Emma Chandler"
date: "5/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
remove(list = ls())
```

Load Libraries
```{r warning=FALSE}
library(ggplot2)
library(lmerTest)
library(dplyr)
library(lme4)
library(car)
```


Load Data
```{r}
Germ <- read.csv("~/horsenettle_2022/data/PollenGerm.csv", header = TRUE)

Pdiam <- read.csv("~/horsenettle_2022/data/PollenDiameter.csv", header = TRUE)
```

Create theme for plots
```{r}
HStheme <- function(){            
  theme_bw()+                          
  theme(axis.text.x = element_text(size = 12), 
        text = element_text(family = "sans"), 
        axis.text.y = element_text(size = 12),
        plot.subtitle = element_text(size = 16, vjust = 1, hjust = 0.5),
        axis.title = element_text(size = 14),
        panel.grid = element_blank(),
        plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
        plot.title = element_text(size = 20, vjust = 1, hjust = 0.5),
        legend.text = element_text(size = 12),
        legend.title = element_blank())
}
```


Sample Size 
```{r}

(sampsize <- Germ %>%
  na.omit() %>% 
  group_by(Region, Treatment) %>% 
  summarize(count = n_distinct(Iden)))

(sampsize2 <- Pdiam %>%
  na.omit() %>% 
  group_by(Region, Treatment) %>% 
  summarize(count = n_distinct(Iden)))

```

Calculate pollen germination
```{r}

# Calculate pollen germination
Germ$germ <- Germ$tubes / Germ$total_grains
```

# Pollen Germination at 40 degrees C
```{r}

germ.m <- glmer(germ ~ Treatment * Region + (1|ID), data = Germ, family = "binomial")

Anova(germ.m)
anova(germ.m, type = 2)
summary(germ.m)  
# write.csv(summary(germ.m)$coefficients, file = "output/Germ_results.csv" )


ggplot(Germ, aes(x = Region, y = germ, fill = Region)) +
  geom_boxplot() +
  labs(y = 'Pollen Germination at 40°C')+
  facet_wrap(~Treatment) +
  scale_fill_manual(values = c("#104E8B", "#CD2626")) +
  HStheme() +
  theme(legend.position = "none")

# Saving graph
# ggsave("figures/PollenGerm.png", width = 7, height = 5, dpi = 300)



# Is there phenotypic plasticity
ggplot(Germ, aes(x = Treatment, y = germ, color = Region)) +
  HStheme() +
  stat_summary(aes(group = Region), fun = mean, geom = "line", size = 1, alpha = 0.7) +
  stat_summary(aes(group = Region), 
               geom = "errorbar",
               fun.data = mean_cl_boot,
               width = 0.1,size = 0.2) +
  # geom_jitter(width = 0.22) +
  labs(y = 'Pollen Germination at 40°C') +
  scale_color_manual(values = c("#104E8B", "#CD2626")) 
  
# Saving graph
# ggsave("figures/PollenGerm_pp.png", width = 7, height = 5, dpi = 300)


```
Pollen germination differed between region, but not between treatments of long-term moderate heat during development. No new results.


## Pollen Size
```{r}

PD.m <- lm(PD_mean ~ Treatment * Region, data = Pdiam)

Anova(PD.m)
anova(PD.m, type = 2)
summary(PD.m)
# write.csv(summary(PD.m)$coefficients, file = "output/PollenDiameter_results.csv" )

ggplot(Pdiam, aes(x = Treatment, y = PD_mean, fill = Treatment)) +
  geom_boxplot() +
  labs(y = "Mean Pollen Diameter (µm)")+
  facet_wrap(~Region) +
  scale_fill_manual(values = c("#7AC5CD", "#FF6A6A")) +
  HStheme() +
  theme(legend.position = "none")

# Saving graph
# ggsave("figures/PollenDaim.png", width = 7, height = 5, dpi = 300)



# Is there phenotypic plasticity
ggplot(Pdiam, aes(x = Treatment, y = PD_mean, color = Region)) +
  HStheme() +
  stat_summary(aes(group = Region), fun = mean, geom = "line", size = 1, alpha = 0.7) +
  stat_summary(aes(group = Region), 
               geom = "errorbar",
               fun.data = mean_cl_boot,
               width = 0.1,size = 0.2) +
  # geom_jitter(width = 0.22) +
  labs(y = "Mean Pollen Diameter (µm)") +
  scale_color_manual(values = c("#104E8B", "#CD2626")) 
  
# Saving graph
# ggsave("figures/PollenGerm_pp.png", width = 7, height = 5, dpi = 300)


```

Pollen size differed between treatments, but not between regions. Pollen that developed in heat had significantly smaller pollen grains. Pollen from both 

